\documentclass{swfcthesis1}

\addbibresource{bb.bib}

\usepackage{mwe}

\begin{document}

\Title{操作系统探索}
\Author{尹志成}
\Advisor{王晓林}
\AdvisorTitle{讲师}
\AdvisorInfo{王晓林，男，49 岁，硕士，讲师，毕业于英国格林尼治大学，分布式计算系统专业。
  现任西南林业大学大数据与智能工程学院教师。执教 Linux、操作系统、网络技术等方面的课程，有丰富的 Linux 教学和系统管理经验。}
\Month{六}
\Year{二〇一八}
\Subject{计算机科学与技术专业}
\Abstract{
操作系统最初的诞生是为了搭配大型机进行各种简单繁重的数字运算，但随着时代的演进，
计算机已经不仅仅作为处理数字运算的机器，其附加价值也越来越被人们看重，
人们在生活中赋予了计算机各种各样的角色：电话，电视机，游戏机等，
使计算机通过软件方式来提高自己的做事效率以及丰富个人的生活。
多道程序系统，分时操作系统，一个个新技术的诞生标志着操作系统越发的完善，
计算机操作系统的体积也不断增大。
但是计算机的发展似乎到了一个瓶颈，工程师不断将各种各样的功能代码加入到系统内核中，
导致系统内核代码量成倍的增长，出现BUG的几率也成倍的增长，
所以，为了探究如何简化操作系统，那么就应该拨开操作系统华丽的外衣，
从历史的迷雾中寻找操作系统的本质，并从底层开始，不断探索并实现各项功能，
最简洁的代码完成一个满足现代各项需求的操作系统。
  }
\Keywords{操作系统，设计，原理，简化}
\Acknowledgments{
  四年时光匆匆而过，解了不多不少的惑。一初听说最怕的人，成了感谢最多的人。

  当过班上班主任的王晓林老师，在我心里仍然是班主任，我想这不止是因为他当过，而是我认为他当过。
  他的认真负责和较真较劲让上过课的每个学生印象深刻，
  他教书教得好，是大家都认同的，而这里的大家还包括一些讨厌他古板作派的同学。
  他的一门课只有一个presentation，学期结束了，presentation也就结束了，
  presentation的内容不跟教学大纲走，在大学课本里也都找不到，
  但是总能在权威的技术书籍里看到影子，也总能在相关知识的学习中联想到并且用到。
  他上课不喜欢教，就喜欢问，然后像个学生一样跟学生讨论来讨论去，
  讨论着讨论着我们就学会了，而且印象深刻。
  他崇尚GNU的自由精神，也不断告诉我们觉得对的就应该不顾一切勇敢的努力的去做。
  他也喜欢干点专权的事，拿着老师的架子逼着全班学生装Linux，也许之前也想不通为什么要这样做，
  但是如果没有这样一个人逼着改变，我想Linux对我只是一门课，而现在Linux是我提高效率的工具。
  
  选择毕业设计导师的时候我没怎么犹豫，我想，对，就是他。
  }
\enTitle{Operating system exploration}
\enAuthor{Zach Yin}
\enAbstract{
  % The initial version of the operating system was to collaborate with simple and heavy-duty digital computing machines. 
  % However, with the evolution of the times, computers have not only been used as machines for processing various operations, 
  % but also added more value with people. With the development of computers, The multi-programming system, 
  % the time-sharing operating system, and the emergence of new technologies mark the increasingly perfect operating system. 
  % However, to explore the operating system, it should not satisfy the existing operating system. 
  % It should open up the gorgeous operating system. Starting from the ground floor, 
  % after a step-by-step exploration, we constantly explored and implemented various functions, 
  % completing an operating system that satisfies modern requirements from the most concise code.

  The initial operation of the operating system was to collaborate with the mainframe to perform various simple and heavy-duty digital operations, 
  but as the times evolved, Computers have not only been used as machines for digital computing, but their added value has also been valued by people.
  People have given the computer a variety of roles in life: telephones, television sets, game consoles, etc.
  Make computers use software to improve their efficiency and enrich their lives.
  The multi-programming system, the time-sharing operating system, and the birth of new technologies mark the increasingly perfect operating system.
  Computer operating systems are also growing in size.
  However, the development of computers seems to be a bottleneck. Engineers continue to add a variety of function codes to the system kernel.
  As a result, the amount of code in the system kernel has increased exponentially, and the probability of a BUG has also multiplied.
  So, in order to explore how to simplify the operating system, you should open up the gorgeous coat of the operating system.
  Look for the essence of the operating system from the fog of history and start from the bottom, constantly exploring and implementing various functions.
  The simplest code completes an operating system that meets all modern requirements.
  }
\enKeywords{Operating System, Design, Principle, simplify}

%%% 下面六行不要动！
\makepreliminarypages% 封面
\frontmatter          
\tableofcontents     % 目录
\listoffigures       % 插图目录
\listoftables        % 表格目录
\mainmatter

% 引言 v
\include{chapters/intro}
% 思路 v
\include{chapters/method}
% 原理 v
\include{chapters/principle}
% 启动 v
\include{chapters/boot}
% 内核 
% \input{chapters/kernel}
\chapter{编写操作系统内核}
  \input{kernel/boot}
  \include{kernel/mem}
  \input{kernel/io}
  \input{kernel/mul}
% 兼容 缺
\include{chapters/compatible}

%%% 正文部分到此结束。下面是『参考文献』、『指导教师简介』、『鸣谢』、『附录』

%% 不要动下面四行！
\Appendix{}
\printbibliography[heading={bibintoc},title={参考文献}] % 输出参考文献
\advisorinfopage{}                 % 输出指导教师简介
\acknowledgmentspage{}             % 输出鸣谢

%%% 下面是附录部分，可以没有。
% 附录
\include{chapters/appendix}

% 程序
\include{chapters/program}

\end{document} % 结束。不要动下面几行！

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
